\chapter{Results and Visualizations}

When we started out the initial core data set contained mostly director sharing data. The process of data collection for this dataset is described in data collection section [cite section]. Interesting insights come about when we dig inside this dataset and try to find how a big entity is connected to another big entity. \\

Interesting results come about when we merged this dataset with family trees and political data that we obtained.  Though list is a bit long, we have tried to document only the best examples here. \\

We have just been able to touch three realms here: corporate, political, entertainment.
Also, we have tried to see family trees to validate nepotistic practices in polictis and businesses.

Idea: show : validate our hypothesis: power house sinteract and mingle among themselves
1. sons, daughters, wives, parents, in-lawas share board of director positions
2. marraiges in nig power houses among big power houses -- link established explicilty
3. business tycoons come baout together to become board of directors
4. fmaily trees for corporates large
5. politcians and their families linked to croporate realm
6. cricketers and their corporate links


\section{Influence Network}

Herw e take example of politcian and business tycoon Naveen Jindal. is directly on the board of 8 companies. For 2 hops, he spans 144 companies. 3 hops: >1800 companies. 4 hops: >13000 companies in the 60000 companies network we have in our DB!  Naveen Jindal is connected to (within 3 hops) Ashok Leyland, Ambuja cements, Reliance Power, Indiabull, ONGC, JP Associates, Idea, Essar, IDFC, Tata Motors, Shriram, Bharti, Max Life, IDBI, Mahindra, BPCL, Network 18, BHEL, Lanco, Maruti Suzuki, ICICI Bank, Infosys, Adani, ITC, Tech Mahindra, Wipro, HDFC, Hinduja, DLF, Indraprastha Gas, Dabur India, Jet Aiarways, JK Lakshmi Cement, ad nauseum. It is as if every big company is connected to the other: really the Power Elites! And to top that, he was an MP for ten years.

[images here]
[can have small small or many]
[naveen jindal ]

\section{intersting directors}
parekh [todo]
lavasa [todo]

\section{media and corporate houses}
Shobhana Bhartia is a very typical case here. Son is also associated. Related to birlas and jindals owners of Ht, rajya sabha MP.
Another example aveek sarkar [todo] 

\section{Family trees}
Ambani
thapar family tree with companies [image]
Also show how spouses also share directorship.
yadav family tree [todo]

\subsection{runawaysa and their families}
modi and mallya [todo]

\section{arts, sports and corpoarte}
bacchan
pretiy jitna
ganguly [todo]
gavaskar [todo]

\section{politics and corporate}
gandhi
sinha
panda, galla metnion
kamalnath
